### 2020-12-24 README.Rmd
added explicit mentio nof applyHS to doprojection  No EWN

  midtime <- (Sys.time())
  applyHS <- mcdahcr   # name the HS/HCR to be used
mseproj <- doprojection(zoneCP,zoneDR,glb,ctrl,projC$projyrs,projC$inityrs)
sauzoneDP <- asSAU(mseproj,sauindex,saunames,B0,exB0)
  endtime <- (Sys.time())
  print(endtime - midtime)
# Now plot some results
  plotC <- function(nsau,saunames,reps,projyrs,plts=c(4,2)) {
    return(list(nsau=nsau,saunames=saunames,reps=reps,projyrs=projyrs,plts=plts))
  }

>>>>

  midtime <- (Sys.time())
mseproj <- doprojection(zoneCP,zoneDR,glb,ctrl,projC$projyrs,applyHS=mcdahcr,projC$inityrs)
sauzoneDP <- asSAU(mseproj,sauindex,saunames,B0,exB0)
  endtime <- (Sys.time())
  print(endtime - midtime)
# Now plot some results
  plotC <- function(nsau,saunames,reps,projyrs,plts=c(4,2)) {
    return(list(nsau=nsau,saunames=saunames,reps=reps,projyrs=projyrs,plts=plts))
  }
